---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(tidyverse)
theme_set(theme_bw())
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300
)
```

# edwards97

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/paleolimbot/edwards97.svg?branch=master)](https://travis-ci.org/paleolimbot/edwards97)
[![Codecov test coverage](https://codecov.io/gh/paleolimbot/edwards97/branch/master/graph/badge.svg)](https://app.codecov.io/gh/paleolimbot/edwards97?branch=master)
[![R-CMD-check](https://github.com/paleolimbot/edwards97/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/paleolimbot/edwards97/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of edwards97 is to implement the Edwards (1997) Langmuir-based semiempirical coagulation model, which predicts the concentration of organic carbon remaining in water after treatment with an Al- or Fe-based coagulant. Methods and example data are provided to optimise empirical coefficients.

This package is experimental, under constant development, and is in no way guaranteed to give accurate predictions (yet).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("paleolimbot/edwards97")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, warning=FALSE}
library(edwards97)

fit_data_alum <- edwards_data("Al")

# optimise coefficients for this dataset
fit <- fit_edwards_optim(fit_data_alum, initial_coefs = edwards_coefs("Al"))

# view fit results
print(fit)
plot(fit)
```

Using the fit, you can make predictions about unknown inputs:

```{r diminishing-returns}
grid <- coagulate_grid(fit, DOC = c(4, 8), UV254 = c(0.2, 0.4)) %>% 
  mutate(label = glue::glue("DOC: {DOC} mg/L, UV254: {UV254} 1/cm"))

diminishing_returns <- grid %>% 
  group_by(label, pH) %>% 
  summarise(dose = dose_of_diminishing_returns(dose, DOC_final, threshold = 0.3 / 10))

ggplot(grid, aes(x = dose, y = pH)) +
  geom_raster(aes(fill = DOC_final)) +
  geom_path(data = diminishing_returns, col = "red", size = 1) +
  facet_wrap(vars(label)) +
  coord_cartesian(expand = FALSE)
```

## References

Edwards, M. 1997. Predicting DOC removal during enhanced coagulation. Journal - American Water Works Association, 89: 78–89. https://doi.org/10.1002/j.1551-8833.1997.tb08229.x
